### 2018-06-21 manuscript.rmd
removed link

---
bibliography: manuscript.bib
csl: current-biology.csl
output:
  github_document: default
  pdf_document:
    latex_engine: xelatex
  word_document: default
---

@@

Each new matrix was analyzed with phylobayes-mpi version 1.8. Analyses were run for 1000 generations, and a `r burnin` generation burnin applied. The resulting tree files and posterior predictive scores were parsed for display with the code in https://github.com/caseywdunn/feuda_2017/manuscript.rmd .

The statistics presented in Supplemental Figures 1 and 2 were parsed from the Feuda *et al.* manuscript into the file `tidy_table_3.tsv` and rendered for display with the code on the source file for this document.

>>>>

---
bibliography: manuscript.bib
csl: current-biology.csl
output:
  pdf_document:
    latex_engine: xelatex
  github_document: default
  word_document: default
---

@@

Each new matrix was analyzed with phylobayes-mpi version 1.8. Analyses were run for 1000 generations, and a `r burnin` generation burnin applied. The resulting tree files and posterior predictive scores were parsed for display with the code in `manuscript.rmd`.

The statistics presented in Supplemental Figures 1 and 2 were parsed from the Feuda *et al.* manuscript into the file `tidy_table_3.tsv` and rendered for display with the code in `manuscript.rmd`.
